Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-15 draft.tex
clarify wording on inside actors best response
adjust restriction 6 and item 1 in defn 2

\item \textit{$B_p^t \geq \mu, \ \forall t>1$: the patron can afford to pay to maintain the status quo.}\footnote{Depending on parameters, one might think that Restriction (5) is more likely to be binding than Restriction (6). If there is great variance in budget between periods for the patron, such as a greatly reduced budget in some period $t> 1$ compared to period $1$, (6) could be the binding constraint.}\label{res:6}

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses given the continuation values induced by the investments of the outside actors. The continuation value from choosing war is the expected future stream of payoffs from the two possible absorbing states net of the cost of war $\left(-\zeta_i +\frac{W_i^t(p_i)+ L_i^t(1-p_i)}{1-\delta}\right)$. Similarly, the continuation value from ceding is $\frac{L_i^t}{1-\de}$ while that for the status quo is $\sum_{s=t}^\infty \de^{t-s} Q_i^t$. Unless otherwise noted below, playing Status Quo is the dynamic best response for both inside actors.

@@

\begin{enumerate}
	\item The patron invests $R_p^t = \max\left\{\frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right),\frac{\omega_s^{t-1}}{1-\de} +\mu - \frac{Q_s^{t-1}}{1-\de},0\right\}$ to augment $Q_s^{t-1}$. Player $c$ invests $R_c^t =0$ to augment $L_s^{t-1}$.

>>>>

\item \textit{$B_p^t \geq \mu, \ \forall t$: the patron can afford to pay to maintain the status quo.}\footnote{Depending on parameters, one might think that Restriction (5) is more likely to be binding than Restriction (6). If there is great variance in budget between periods for the patron, such as a greatly reduced budget in some period $t> 1$ compared to period $1$, (6) could be the binding constraint.}\label{res:6}

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses given the continuation values induced by the investments of the outside actors. The continuation value from choosing war is the expected future stream of payoffs from the two possible absorbing states net of the cost of war $\left(-\zeta_i +\frac{W_i^t(p_i)+ L_i^t(1-p_i)}{1-\delta}\right)$. Similarly, the continuation value from ceding is $\frac{L_i^t}{1-\de}$ while that for the status quo is $\sum_{s=t}^\infty \de^{t-s} Q_i^t$. Unless otherwise noted below, playing Status Quo is the best response for both inside actors in terms of continuation values.

@@

\begin{enumerate}
	\item The patron invests $R_p^t = \max\left\{\frac{\beta}{1-\de} - \left( Q_s^{t-1} - \mu - L_s^{t-1}\right),\omega_s^{t-1} +\mu - Q_s^{t-1},0\right\}$ to augment $Q_s^{t-1}$. Player $c$ invests $R_c^t =0$ to augment $L_s^{t-1}$.
